Summary Tables

### 2020-07-15 summary_tables.Rmd
Floating TOC

---
title: "Summary Tables"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    theme: united
---

@@

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
cities <- c('accra','sao_paulo','delhi','bangalore', 'santiago', 'belo_horizonte', 'buenos_aires', 'mexico_city','bogota', 'cape_town', 'vizag')

@@

|accra|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 96.7|66.2|2.0 |
| bicycle | 0.6|0.3|0.4 |
| car | 1.0|10.4|16.9 |
| motorcycle | 0.2|0.9|2.7 |
| bus | 0.0|18.6|69.4 |

|sao_paulo|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 65.4|6.9|2.9 |
| bicycle | 0.7|0.9|0.3 |
| car | 22.2|41.9|27.2 |
| motorcycle | 1.3|2.7|3.5 |
| bus | 9.7|43.0|35.8 |

|delhi|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 84.3|11.1|0.8 |
| bicycle | 1.9|7.9|3.6 |
| car | 1.9|14.7|19.6 |
| motorcycle | 5.6|31.9|25.3 |
| bus | 0.7|19.7|35.5 |

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 89.7|28.6|1.2 |
| bicycle | 2.6|10.9|0.9 |
| car | 0.8|5.0|4.9 |
| motorcycle | 4.8|37.3|48.2 |
| bus | 0.6|8.3|29.3 |

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 92.5|29.7|0.3 |
| bicycle | 1.5|10.5|2.5 |
| car | 5.4|42.3|27.4 |
| motorcycle | 0.0|0.6|0.7 |
| bus | 0.0|3.1|36.0 |

|belo_horizonte|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 91.7|36.0|0.6 |
| bicycle | 0.4|3.6|1.0 |
| car | 7.2|39.9|38.9 |
| motorcycle | 0.2|6.6|7.3 |
| bus | 0.0|0.9|39.4 |

|buenos_aires|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 95.9|32.9|0.2 |
| bicycle | 3.0|10.1|1.5 |
| car | 0.5|24.1|25.4 |
| motorcycle | 0.0|2.2|1.7 |
| bus | 0.6|27.4|49.9 |

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 95.4|38.1|0.3 |
| bicycle | 0.8|7.7|1.3 |
| car | 2.3|23.9|28.6 |
| motorcycle | 0.0|3.3|1.9 |
| bus | 0.3|19.0|48.2 |

@@

|vizag|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 81.4|19.6|0.1 |
| bicycle | 3.9|7.6|1.9 |
| car | 0.6|2.5|2.2 |
| motorcycle | 9.6|25.4|22.9 |
| bus | 0.1|21.7|56.1 |

@@

trip_prop <- trip_prop %>% dplyr::filter(stage_mode != "row_sums") %>% mutate_if(is.factor, ~ as.numeric(as.character(.x))) %>% janitor::adorn_totals('row')

>>>>

---
title: "Summary Tables"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
---

@@

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
cities <- c('accra','sao_paulo','delhi','bangalore', 'santiago', 'belo_horizonte', 'buenos_aires', 'bogota',
             'mexico_city', 'vizag')

@@

|accra|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 98.1|72.3|2.9 |
| bicycle | 0.5|0.3|0.5 |
| car | 1.0|9.0|17.1 |
| motorcycle | 0.0|0.0|0.0 |
| bus | 0.0|15.0|64.4 |

|sao_paulo|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 62.2|7.2|3.0 |
| bicycle | 0.7|0.9|0.3 |
| car | 21.0|42.9|28.7 |
| motorcycle | 1.3|2.9|3.8 |
| bus | 13.3|39.2|32.7 |

|delhi|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 84.4|10.1|0.9 |
| bicycle | 2.0|7.6|3.7 |
| car | 2.4|17.3|21.4 |
| motorcycle | 5.6|30.1|26.5 |
| bus | 0.7|24.7|32.7 |

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 74.9|23.0|1.0 |
| bicycle | 2.3|9.8|1.1 |
| car | 1.0|4.4|6.4 |
| motorcycle | 5.1|33.9|63.2 |
| bus | 15.1|24.3|25.0 |

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 88.4|23.2|0.3 |
| bicycle | 3.5|8.7|2.3 |
| car | 7.2|45.5|35.5 |
| motorcycle | 0.1|1.4|1.4 |
| bus | 0.3|10.1|29.6 |

|belo_horizonte|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 91.7|34.7|0.6 |
| bicycle | 0.4|3.5|1.0 |
| car | 7.2|38.4|39.5 |
| motorcycle | 0.2|6.3|7.4 |
| bus | 0.1|4.5|38.4 |

|buenos_aires|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 96.5|33.8|0.2 |
| bicycle | 2.4|8.3|1.2 |
| car | 0.5|24.8|25.7 |
| motorcycle | 0.0|1.8|1.5 |
| bus | 0.5|27.7|50.1 |

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 95.3|37.6|0.3 |
| bicycle | 0.8|7.4|1.2 |
| car | 2.4|24.9|29.6 |
| motorcycle | 0.0|3.1|1.9 |
| bus | 0.3|18.8|47.1 |

@@

|vizag|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 80.6|18.3|0.1 |
| bicycle | 3.9|7.2|2.0 |
| car | 0.6|2.3|2.4 |
| motorcycle | 9.5|23.8|25.0 |
| bus | 1.2|27.5|56.0 |

@@

trip_prop <- trip_prop %>% dplyr::filter(stage_mode != "row_sums") %>% mutate_at(2:ncol(trip_prop), ~ as.numeric(as.character(.x))) %>% janitor::adorn_totals('row')
